---
title: "p8105_hw1_lq2250"
author: "Lanlan_Qing"
date: "2024-09-12"
output: github_document
---
# This is a Rmarkdown file of Homework1

## Problem 1
### Loading data
```{r package_load}
data("penguins", package = "palmerpenguins")
```
### Extract information
```{r data}
num_row = nrow(penguins)
num_col = ncol(penguins)
library(tidyverse)
mean_flipper_len = format(round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE),2))
```
### Results
The *size* of the the dataset is 
**`r num_row`** rows and **`r num_col`** columns.<br>
The *mean flipper length* is 
**`r mean_flipper_len`**mm.

### The scatterplot of flipper length(mm) v.s bill length(mm)
```{r scatterplot_flip_vs_bill}
library(ggplot2)
ggplot(penguins, 
       aes(x = bill_length_mm, y = flipper_length_mm ))+
  geom_point(aes(color = species))
ggsave('scatterplot_flipper_vs_bill.pdf')
```
## Problem 2

### Create the dataframe
```{r dataframe}
norm_sample = rnorm(10)
cha_vec = c('Red','Yellow','Red','White','Red','Yellow','Yellow','White','White','White')
log_vec = c(norm_sample > 0)
fac_vec = factor(cha_vec, nmax = 3)
data_frame = data.frame(norm_sample,
                        log_vec,
                        cha_vec,
                        fac_vec)
```
### Take the mean of each variable
```{r mean_calculation}
num_mean = mean(pull(data_frame, norm_sample))
log_mean = mean(pull(data_frame, log_vec))
cha_mean = mean(pull(data_frame, cha_vec))
fac_mean = mean(pull(data_frame, fac_vec))
```

### Results
The mean of *random sample* is
**`r num_mean`**.<br>
The mean of *logical vector* is
**`r log_mean`**.<br>
The mean of *character vector* is
**`r cha_mean`**.<br>
The mean of *factor vector* is
**`r fac_mean`**.<br>

**Q: Try to take the mean of each variable in your dataframe. What works and what doesn’t?** <br>
The mean of a **numeric vector** like sample can directly return a valid result. <br>
The **logical vector** should return a result of NA, but it has internal numeric value where "TRUE" returns to 1 and "FALSE" returns to 0, so there's still numeric mean calculated.<br>
**Character** and **factor vectors** are composed of non-numeric elements, which are not applicable for mean calculation.

### Application of numeric function
```{r function_apply}
log_mean_num = as.numeric(log_mean)
cha_mean_num = as.numeric(cha_mean)
fac_mean_num = as.numeric(fac_mean)
```
**Q: What happens, and why? Does this help explain what happens when you try to take the mean?** <br>
**Logical**: TRUE becomes 1 and FALSE becomes 0.<br>
**Character**: Results in NA with a warning, as non-numeric characters can't be directly converted to numeric. <br>
**Factor**: The function converts factors to their internal numeric levels.