---
title: "p8105_hw1_lq2250"
author: "Lanlan_Qing"
date: "2024-09-12"
output: github_document
---
# This is a Rmarkdown file of Homework1

## Problem 1
### Loading data
```{r package_load}
data("penguins", package = "palmerpenguins")
```
### Extract information
```{r data}
num_row = nrow(penguins)
num_col = ncol(penguins)
library(tidyverse)
mean_flipper_len = format(round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE),2))
```
### Results
The **size** of the the dataset is 
**`r num_row`** rows and **`r num_col`** columns.<br>
The **mean flipper length** is 
**`r mean_flipper_len`**mm.

### The scatterplot of flipper length(mm) v.s bill length(mm)
```{r scatterplot_flip_vs_bill}
library(ggplot2)
ggplot(penguins, 
       aes(x = bill_length_mm, y = flipper_length_mm ))+
  geom_point(aes(color = species))
ggsave('scatterplot_flipper_vs_bill.pdf')
```
## Problem 2

### Create the dataframe
```{r dataframe}
norm_sample = rnorm(10)
data_frame = data.frame(norm_sample,
                        log_vec = c(norm_sample > 0),
                        cha_vec = c('Red','Yellow','Blue','White','Pink',
                                    'Orange','Black','Brown','Violet','Grey'),
                        fac_vec = c('High', 'Low', "Medium", 'High', 'Low', 
                                    'Low', 'High', 'Low', "Medium", "High")
)
```
```{r mean_calculation}
num_mean = mean(pull(data_frame, norm_sample))
log_mean = mean(pull(data_frame, log_vec))
cha_mean = mean(pull(data_frame, cha_vec))
fac_mean = mean(pull(data_frame, fac_vec))
```

### Results
The mean of *random sample* is
**`r num_mean`**.<br>
The mean of *logical vector* is
**`r log_mean`**.<br>
The mean of *character vector* is
**`r cha_mean`**.<br>
The mean of *factor vector* is
**`r fac_mean`**.

### Application of numeric function
```{r function_apply}
log_mean_num = as.numeric(log_mean)
cha_mean_num = as.numeric(cha_mean)
fac_mean_num = as.numeric(fac_mean)
```
