---
title: "p8105_hw1_lq2250"
author: "Lanlan_Qing"
date: "2025-09-16"
output: github_document
---

```{r echo = FALSE}
# Load the library
library(moderndive)
library(tidyverse)
library(ggplot2)
```

## Problem 1
```{r}
# Load the dataset as ejw_df
data("early_january_weather")

ejw_df = early_january_weather
temp = pull(ejw_df, temp)
```

### Description:

The dataset of "early_january_weather" contains **`r names(ejw_df)`** variables.

The dataset is composed of `r nrow(ejw_df)` rows and `r ncol(ejw_df)` columns.

The mean temperature is `r round(mean(temp),digits = 2)`.

```{r}
# Made the scatter plot of temp(y) vs time_hour(x)
scatter_plot = ggplot(data = ejw_df,
                      aes(x = time_hour,
                          y = temp,
                          color = humid)) +
  geom_point() +
  labs(title = "Temperature vs. Time",
       x = "Date",
       y = "Temperature",
       color = "Humidity")

ggsave("Plots/scatter_plot.jpg")
print(scatter_plot)
```

### Description:

The temperature and time seem to be **positively related**. While time is increasing, temperature also trends to increase.

## Problem 2
```{r}
# Identify the variables
sample_num = rnorm(10)
log_vec = sample_num > 0
cha_vec = c("boy", "girl", "boy", "girl", "girl", "boy", "girl", "boy", "boy", "boy")
fac_vec = factor(c("low", "low", "high", "medium", "high", "high", "medium", "medium", "medium", "medium" ))
sample_df = data.frame(sample_num,
                     log_vec,
                     cha_vec,
                     fac_vec 
                     )
```

The mean of each variable in my data frame is:

 - a random sample of size 10 from a standard Normal distribution: `r round(mean(pull(sample_df, sample_num)), digits = 2)`
 
 - a logical vector indicating whether elements of the sample are greater than 0: `r mean(pull(sample_df, log_vec))`
  
 - a character vector of length 10: `r mean(pull(sample_df, cha_vec))`
   
 - a factor vector of length 10, with 3 different factor “levels”: `r mean(pull(sample_df, fac_vec))`
 
**Q. What works and what doesn’t?**

Only the forward two variables of **random sample** and **logical vector** work. The **character factor** and **factor vector** do not.

```{r echo = FALSE}
log_mean = mean(as.numeric(pull(sample_df, log_vec)))
cha_mean = mean(as.numeric(pull(sample_df, cha_vec)))
fac_mean = mean(as.numeric(pull(sample_df, fac_vec)))
```

**Q: What happens, and why? Does this help explain what happens when you try to take the mean?**

 - Logical: TRUE becomes 1 and FALSE becomes 0.
 
 - Character: Results in NA with a warning, as non-numeric characters can't be directly converted to numeric. 
 
 - Factor: The function converts factors to their internal numeric levels.
